---
title: |
  | Developing Data Products - Project One
author: "Raed Abdel Sater"
date: "November 20, 2017"
output: html_document
---

```{r setup, include=FALSE, results='asis'}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

### A. Synopsis

The goal of the Project is to Create a web page using R Markdown that features a map created with Leaflet.Host the webpage on either GitHub Pages, RPubs, or NeoCities.

The webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!


### B. Data Processing
####   Downloading, Unzipping and loading Database

My Current Location in Montreal next to the famous mountain of Mount Royal


####      **Displaying Location and Printing the map**

```{r}
library(knitr)
library(leaflet)
library(dplyr)
```

```{r}
   myDate <- Sys.time()
   print(myDate)
```

```{r}
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=45.495166, lng=-73.580299, popup="My Home, Montreal")
  
m  # Print the map
```



